A GPU Sonar Simulator for Automatic Target Recognition

### 2014-04-29 UAM2014/Article/article.tex
la2pdf commit - 2014:04:28	14:42:31	(Mon28.Apr)
la2pdf commit - 2014:04:28	15:44:10	(Mon28.Apr)
...
la2pdf commit - 2014:04:29	10:02:13	(Tue29.Apr)

% Tune floats
\renewcommand{\topfraction}{0.9}  % max fraction of floats at top
\renewcommand{\bottomfraction}{0.8} % max fraction of floats at bottom
%   Parameters for TEXT pages (not float pages):
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}     % 2 may work better
\setcounter{dbltopnumber}{2}    % for 2-column pages
\renewcommand{\dbltopfraction}{0.9} % fit big float above 2-col. text
\renewcommand{\textfraction}{0.07}  % allow minimal text w. figs
%   Parameters for FLOAT pages (not text pages):
\renewcommand{\floatpagefraction}{0.85}  % require fuller float pages
% N.B.: floatpagefraction MUST be less than topfraction !!
\renewcommand{\dblfloatpagefraction}{0.85} % require fuller float pages

@@

@@

@@

\begin{figure}[tp]\centering%
\begin{subfigure}[t]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/data_cylinder_submerged.svg}%
\caption{SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.}\label{data_sylinder}%
\end{subfigure}
\end{figure}

>>>>

% Tune floats
\renewcommand{\topfraction}{0.9}  % max fraction of floats at top
\renewcommand{\bottomfraction}{0.8} % max fraction of floats at bottom
%   Parameters for TEXT pages (not float pages):
\setcounter{topnumber}{1}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}     % 2 may work better
\setcounter{dbltopnumber}{2}    % for 2-column pages
\renewcommand{\dbltopfraction}{0.9} % fit big float above 2-col. text
\renewcommand{\textfraction}{0.07}  % allow minimal text w. figs
%   Parameters for FLOAT pages (not text pages):
\renewcommand{\floatpagefraction}{0.85}  % require fuller float pages
% N.B.: floatpagefraction MUST be less than topfraction !!
\renewcommand{\dblfloatpagefraction}{0.85} % require fuller float pages

@@

We have developed fast a synthetic aperture sonar (SAS) simulator that run on graphics processing units (GPUs)  using a combination of OpenGL for graphics processing and OpenCL for post-processing. This implementation resembles the SIGMAS+ simulator developed at the NATO Undersea Research Centre (NURC). They both take advantage of graphics processing to render a 2D image from 3D models and assume a Lambertian scattering model.

@@

The basic idea behind using a graphics

OpenGL is a multi-platform application programming interface (API) for rendering 2D and 3D vector graphics.

@@

The simulator performance were tested on an image from the HISAS 1030 synthetic aperture sonar mounted on the HUGIN AUV. Out of the objects in the scene we selected a 2.6\;m cylinder that was slightly buried in the sea sediments (Fig. \ref{data_sylinder}).

\begin{figure}[tp]\centering%
\begin{subfigure}[t]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/data_cylinder_submerged.svg}%
\caption{SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.}\label{data_sylinder}%
\end{subfigure}
\begin{subfigure}[t]{.5\linewidth-\imgspacing/2}
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
\caption{Cylinder simulation with parameters adapted to fit the SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.}%
\end{subfigure}
\caption{}
\end{figure}

\setcounter{topnumber}{2}
